\bf An HMM-based part-of-speech tagger for Turkish

### 2015-11-17 proposal/proposal.tex
Update proposal

@@

% Briefly survey the most salient prior work that relates to the problem you wish
% to solve. This section should cite relevant sources. This section should be at
% least one to two paragraphs in length.
The most important advancement in the computational linguistics of Turkish is
the NLP framework ``Zemberek'' by \citet{akin2007zemberek}. Although it started
out as an NLP tool for the Turkish language, Zemberek moved on to become a
a tool for processing all Turkic languages. Zemberek has been immensely useful
for linguistic research on Turkish.

@@

Most of the work relating to the computational processing of Turkish deal with
Turkish morphology since Turkish is a morphologically rich language analyzing
the morphology seems to be the more salient problem e
\section{Proposal}

I will be implementing a part-of-speech tagger for the Turkish language. As
mention in section~\ref{sec:related_work} I will be mostly focusing on parts-of-speech
of words and will not be accounting for morphology. There are problems with this
approach but this project aims to be a starting point for further research.

>>>>

\newcommand{\hmmURL}{https://hackage.haskell.org/package/hmm-0.2.1.1/docs/Data-HMM.html}

@@

% Briefly survey the most salient prior work that relates to the problem you wish
% to solve. This section should cite relevant sources. This section should be at
% least one to two paragraphs in length.
The most important advancement in the computational linguistics of Turkish is
the NLP framework ``Zemberek'' by \citet{akin2007zemberek} that has been
immensely useful for both research and applications of Turkish NLP. Although it started
out as an NLP tool for the Turkish language, Zemberek moved on to become a
a tool for processing all Turkic languages. Zemberek

@@

Most of the literature relating to the computational processing of Turkish
pertain primarily to Turkish morphology---compared to the complexity of Turkish
morphology, its syntax seems to be a less interesting problem.
\section{Proposal}

I will be implementing a part-of-speech tagger for the Turkish language. As
mentioned in section~\ref{sec:related_work} I will be mostly focusing on parts-of-speech
of words\footnote{I base my defition of a ``word'' on the orthographic space in
  most of the cases. Some of the exceptions to this are Turkish reduplication
  that have the POS ``Dup''} and will not be accounting for morphology. There are problems with this
approach but this project aims to be a starting point for further research.

For programming the POS tagger I will be using Haskell, a statically-typed and purely
functional programming language. I will be using the
\href{\hmmURL}{\texttt{Data.HMM}} package for
Haskell. The data, that is probably the most important component of this
project, comes from the METU-Sabanc\i treebank built by
\citet{oflazer2003building}. I will be stripping the POS tag for each word from
the corpus and will use them to train HMM's.
